%!TEX root = ./0_main.tex
\section{Literature}\label{sec: literature}

Our paper is related to several strands of the literature.

\paragraph{School choice.} Starting with \cite{Abdulkadiroglu2003}, a large body of literature has studied different elements of the school choice problem, including the use of different mechanisms such as DA, Boston, and TTC~\citep{abdulkadirouglu2005boston}; the use of different tie-breaking rules~\citep{Arnosti_2015,Ashlagi_2019}; the handling of multiple and potentially overlapping quotas; the addition of affirmative action policies; and the implementation in many school districts and countries.

 \cite{Abdulkadiroglu2003}, \citep{abdulkadirouglu2005new}, \citep{abdulkadirouglu2005boston}.  Barcelona \citep{calsamiglia2014illusion}, Amsterdam \citep{gautier2016eerste} and Chile~\cite{Correa_2022} have implemented centralized school choice systems using some variant of DA, BM, or Top-Trading Cycles (TTC). \cite{Abdulkadiroglu2003} also initiated a large literature that theoretically analyzes the school choice problem.

\paragraph{Optimization in stable matching.}
\begin{itemize}
  \item Starters: \cite{gusfield1989stable, vate1989linear,rothblum1992characterization,roth1993stable}
  \item Formulations: \cite{baiou2000stable}, \cite{kwanashie2014integer}, \cite{agoston2016integer}, \cite{agoston_etal2021}, \cite{delorme2019mathematical}.
  \item Alternative objectives: \cite{shi2016}, \cite{Ashlagi_2016}, \cite{bodon2020}, \cite{bobbio22}
\end{itemize}


\paragraph{Siblings.} \cite{Dur_2022}, \cite{Dur_2019}, \cite{Correa_2022}

\paragraph{Complementarities.}
