\bibliographystyle{informs2014}
\begin{thebibliography}{36}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }

\bibitem[{Abdulkadiroglu et~al.(2017)Abdulkadiroglu, Che, Pathak, Roth,
  \protect\BIBand{} Tercieux}]{abdulkadiroglu2017minimizing}
Abdulkadiro{\u{g}}lu A, Che YK, Pathak PA, Roth AE, Tercieux O (2017) Minimizing
  justified envy in school choice: The design of New Orleans' OneApp. NBER working paper.

\bibitem[{Abdulkadiro{\u{g}}lu et~al.(2011)Abdulkadiro{\u{g}}lu, Che,
  \protect\BIBand{} Yasuda}]{abdulkadirouglu2011resolving}
Abdulkadiro{\u{g}}lu A, Che YK, Yasuda Y (2011) Resolving conflicting
  preferences in school choice: ``The Boston mechanism'' reconsidered.
  \emph{American Economic Review} 101(1):399--410.

\bibitem[{Abdulkadiro{\u{g}}lu et~al.(2015)Abdulkadiro{\u{g}}lu, Che,
  \protect\BIBand{} Yasuda}]{ACY15}
Abdulkadiro{\u{g}}lu A, Che YK, Yasuda Y (2015) Expanding ``choice'' in school
  choice. \emph{American Economic Journal: Microeconomics} 7(1):1--42.

\bibitem[{Abdulkadiro{\u{g}}lu et~al.(2005{\natexlab{a}})Abdulkadiro{\u{g}}lu,
  Pathak, \protect\BIBand{} Roth}]{abdulkadirouglu2005new}
Abdulkadiro{\u{g}}lu A, Pathak PA, Roth AE (2005{\natexlab{a}}) The {N}ew
  {Y}ork {C}ity high school match. \emph{American Economic Review} 95(2):364--367.

\bibitem[{Abdulkadiro{\u{g}}lu et~al.(2009)Abdulkadiro{\u{g}}lu, Pathak,
  \protect\BIBand{} Roth}]{Abdulkadiroglu2009}
Abdulkadiro{\u{g}}lu A, Pathak PA, Roth AE (2009) Strategy-proofness versus
  efficiency in matching with indifferences: redesigning the {N}ew {Y}ork
  {C}ity high school match. \emph{American Economic Review} 99(5):1954--78.

\bibitem[{Abdulkadiro{\u{g}}lu et~al.(2005{\natexlab{b}})Abdulkadiro{\u{g}}lu,
  Pathak, Roth, \protect\BIBand{} S{\"o}nmez}]{abdulkadirouglu2005boston}
Abdulkadiro{\u{g}}lu A, Pathak PA, Roth AE, S{\"o}nmez T (2005{\natexlab{b}})
  The {B}oston public school match. \emph{American Economic Review} 95(2):368--371.

\bibitem[{Abdulkadiro{\u{g}}lu \protect\BIBand{}
  S{\"o}nmez(2003)}]{Abdulkadiroglu2003}
Abdulkadiro{\u{g}}lu A, S{\"o}nmez T (2003) School choice: A mechanism design
  approach. \emph{American Economic Review} 93(3):729--747.

\bibitem[{Anderson et~al.(2015)Anderson, Ashlagi, Gamarnik, Rees, Roth, Sönmez \protect\BIBand{} {\"{U}}nver}]{anderson2015}
    Anderson, R, Ashlagi, I, Gamarnik, G, Rees, M, Roth, AE, Sönmez, T, {\"{U}}nver, M (2018) Kidney Exchange and the Alliance for Paired Donation: Operations Research Changes the Way Kidneys Are Transplanted. \emph{Journal of Applied Analytics} 45(1): 26--42.

\bibitem[{Andersson et~al.(2018)Andersson, Dur, Ertemel \protect\BIBand{}
    Kesten}]{andersson2018}
  Andersson T, Dur U, Ertemel S, Kesten Onur (2018) Sequential School Choice with Public and Private Schools. \emph{Working paper}.

\bibitem[{Alon et~al.(2018)Alon, Bronfman, Hassidim \protect\BIBand{}
      Romm}]{alon2018}
    Alon N, Bronfman S, Hassidim A, Romm, A (2018) Redesigning the Israeli Medical
    Internship Match. \emph{ACM Transactions on Economics and Computation} 6(3):1--28.

\bibitem[{Arnosti(2015)}]{Arnosti15}
Arnosti N (2015) Short lists in centralized clearinghouses. \emph{Proceedings
  of the Sixteenth ACM Conference on Economics and Computation}, EC '15.

\bibitem[{Ashlagi et~al.(2014)Ashlagi, Braverman, \protect\BIBand{}
  Hassidim}]{ashlagi2014}
Ashlagi I, Braverman M, Hassidim A (2014) Stability in large matching markets
  with complementarities. \emph{Operations Research} 62(4):713--732.

\bibitem[{Ashlagi et~al.(2019)Ashlagi, Nikzad, \protect\BIBand{}
  Romm}]{ashlagi2015assigning}
Ashlagi I, Nikzad A, Romm AI (2019) Assigning more students to their top
  choices: A comparison of tie-breaking rules. \emph{Games and Economic Behavior} 115:167--187.

\bibitem[{Ashlagi et~al.(2014b)Ashlagi, \protect\BIBand{} Shi}]{ashlagi2014b}
Ashlagi, Itai and Shi, Peng (2014{\natexlab{b}}) Improving community cohesion in school choice via correlated-lottery implementation. \emph{Operations Research} 62(6):1247--1264.

\bibitem[{Ayg{\"{u}}n et~al.(2017)Ayg{\"{u}}n, \protect\BIBand{} Turhan}]{Aygun2017}
Ayg{\"{u}}n, Orhan and Turhan, Bertan (2017) Large-scale affirmative action in school choice: Admissions to IITs in India. \emph{American Economic Review P\&P} 107(5):210--213.

\bibitem[{Ayg{\"{u}}n et~al.(2020)Ayg{\"{u}}n, \protect\BIBand{} Turhan}]{Aygun2020}
Ayg{\"{u}}n, Orhan and Turhan, Bertan (2020) Dynamic reserves in matching markets. \emph{Journal of Economic Theory} 188:1--29.

\bibitem[{Azevedo \protect\BIBand{} Leshno(2016)}]{AL16}
  Azevedo EM, Leshno JD (2016) A supply and demand framework for two-sided matching markets. \emph{Journal of Political Economy} 124(5):1235--1268.

\bibitem[{Ba{\"\i}ou \protect\BIBand{} Balinski(2004)}]{baiou2004student}
Ba{\"\i}ou M, Balinski M (2004) Student admissions and faculty recruitment.
  \emph{Theoretical Computer Science} 322(2):245--265.

\bibitem[{Balinski \protect\BIBand{} Ratier(1997)}]{balinski1997stable}
Balinski M, Ratier G (1997) Of stable marriages and graphs, and strategy and
  polytopes. \emph{SIAM review} 39(4):575--604.

\bibitem[{Baswana et~al.(2019)Baswana, Chakrabarti, Chandran, Kanoria \protect\BIBand{} Patange(2019)}]{baswana2019}
  Baswana, Surender and Chakrabarti, Partha Pratim and Chandran, Sharat and Kanoria, Yashodhan and Patange, Utkarsh (2019) Of stable marriages and graphs, and strategy and
    polytopes. \emph{Journal of Applied Analytics} 49(5):338--354.

\bibitem[{Bellei(2013)}]{bellei2013estudio}
Bellei C (2013) El estudio de la segregaci{\'o}n socioecon{\'o}mica y
  acad{\'e}mica de la educaci{\'o}n chilena. \emph{Estudios pedag{\'o}gicos} 39(1):325--345.

\bibitem[{Bir\'o(2008)}]{biro2008}
  Bir\'o, P (2008) Student Admissions in Hungary as Gale and Shapley Envisaged. \emph{Working paper}. 1--7.

\bibitem[{Bodoh-Creed(2020)}]{bodon2020}
  Bodoh-Creed, AL (2020) Optimizing for distributional goals in school choice problems. \emph{Management Science} 66(8): 3657--3676.

\bibitem[{Calsamiglia \protect\BIBand{} G{\"u}ell(2018)}]{calsamiglia2014illusion}
Calsamiglia C, G{\"u}ell M (2018) Priorities in School Choice: The Case of the Boston Mechanism in Barcelona. \emph{Journal of Public Economics} 163:20--36.

\bibitem[{Combe(2018)}]{combe18}
Combe, J (2018) Teacher Assignment and Minimal Envy Mechanisms. \emph{SSRN working paper}.

\bibitem[{Combe et~al.(2016)Combe, Tercieux \protect\BIBand{} Terrier(2016)}]{combe16}
Combe, J and Tercieux, O and Terrier, C (2016) The Design of Teacher Assignment: Theory and Evidence.
  \emph{Discussion paper}.


\bibitem[{De~Haan et~al.(2015)De~Haan, Gautier, Oosterbeek, \protect\BIBand{}
  Van~der Klaauw}]{de2015performance}
De~Haan M, Gautier PA, Oosterbeek H, Van~der Klaauw B (2015) The performance of
  school assignment mechanisms in practice. Technical report, Institute for the
  Study of Labor (IZA), Bonn.

\bibitem[{Delacr\'etaz(2020)}]{delacretaz20}
 Delacr\'etaz, D (2020) Processing Reserves Simultaneously.
\emph{Working paper}.


\bibitem[{Dubins \protect\BIBand{} Freedman(1981)}]{DF81}
Dubins LE, Freedman DA (1981) Machiavelli and the Gale-Shapley algorithm.
  \emph{The American Mathematical Monthly} 88(7):485--494.

\bibitem[{Dur et~al.(2016{\natexlab{a}})Dur, Duke, Parag, Pathak,
  \protect\BIBand{} S{\"{o}}nmez}]{Duretal2016JPE}
Dur U, Duke S, Parag K, Pathak PA, S{\"{o}}nmez T (2016{\natexlab{a}}) {Reserve
  design: Unintended consequences and the demise of Boston's walk zones}.
  \emph{Journal of Political Economy} 126(6):2457--2479.

\bibitem[{Dur et~al.(2016{\natexlab{b}})Dur, Pathak, \protect\BIBand{}
  S{\"{o}}nmez}]{Dur2016}
Dur U, Pathak PA, S{\"{o}}nmez T (2016{\natexlab{b}}) {Explicit vs. statistical preferential treatment in affirmative action: Theory and evidence from Chicago's exam schools}. \emph{NBER working paper}.

\bibitem[{Dur et~al.(2019{\natexlab{b}})Dur, Morril, \protect\BIBand{} Phan}]{Dur2019}
Dur, Umut and Morrill, Thayer and Phan, William (2019) {Family Ties: School Assignment With Siblings}. \emph{SSRN working paper}.

\bibitem[{Dur \protect\BIBand{} Wiseman(2019)}]{dur2019b}
Dur, Umut, and Wiseman, Thomas (2019) School choice with neighbors. \emph{Journal of Mathematical Economics} 83:101--109.

\bibitem[{Ehlers(2010)}]{ehlers2010}
Ehlers L (2010) {School Choice with Control}. Cahier 13-2010, CIREQ.

\bibitem[{Ehlers et~al.(2014)Ehlers, Hafalir, Yenmez, \protect\BIBand{}
  Yildirim}]{ehlers2014school}
Ehlers L, Hafalir IE, Yenmez MB, Yildirim MA (2014) School choice with
  controlled choice constraints: Hard bounds versus soft bounds. \emph{Journal
  of Economic Theory} 153:648--683.

\bibitem[{Gale \protect\BIBand{} Shapley(1962)}]{GaleShapley62}
Gale D, Shapley LS (1962) College admissions and the stability of marriage.
  \emph{The American Mathematical Monthly} 69(1):9--15.

\bibitem[{Gautier et~al.(2016)Gautier, De~Haan, Van Der~Klaauw,
  \protect\BIBand{} Oosterbeek}]{gautier2016eerste}
Gautier PA, De~Haan M, Van Der~Klaauw B, Oosterbeek H (2016) Eerste analyse
  matching en loting voortgezet onderwijs amsterdam 2016. Working paper.

\bibitem[{Gonczarowski et~al.(2019)Gonczarowski, Nisan, Kovalio,
    \protect\BIBand{} Romm}]{gonczarowski19}
  Gonczarowski, Yannai A and Nisan, Noam and Kovalio, Lior and Romm, Assaf (2019) Matching for the Israeli "Mechinot" Gap-Year Programs. \emph{SSRN working paper}.

\bibitem[{Guillen \protect\BIBand{} Kesten(2012)}]{guillen2012}
Guillen, P and Kesten, O (2012) Matching Markets with Mixed Ownership: The Case for a Real-life Assignment Mechanism. \emph{International Economic Review} 53(3):1027--1046.


\bibitem[{Hafalir et~al.(2013)Hafalir, Yenmez, \protect\BIBand{}
  Yildirim}]{Hafalir2013a}
Hafalir IE, Yenmez MB, Yildirim MA (2013) {Effective affirmative action in school choice}. \emph{Theoretical Economics} 8(2):325--363.

\bibitem[{Hatfield \protect\BIBand{} Milgrom(2005)}]{hatfield2005matching}
Hatfield JW, Milgrom PR (2005) Matching with contracts. \emph{American Economic
  Review} 95(4):913--935.


\bibitem[{Hassidim et~al.(2018)Hassidim, Romm \protect\BIBand{}
    Shorrer}]{hassidim2018}
  Hassidim, A, Romm, A, Shorrer, R (2018) Need vs. merit: The large core of college admissions markets. \emph{Working paper}.

\bibitem[{Kamada \protect\BIBand{} Kojima(2015)}]{Kamada2015}
Kamada Y, Kojima F (2015) {Efficient matching under distributional constraints:
  Theory and applications}. \emph{American Economic Review} 105(1):67--99.

\bibitem[{Kojima(2012)}]{Kojima2012b}
Kojima F (2012) {School choice: Impossibilities for affirmative action}.
  \emph{Games and Economic Behavior} 75(2):685--693.

\bibitem[{Kojima et~al.(2013)Kojima, Pathak, \protect\BIBand{}
  Roth}]{kojima2013matching}
Kojima F, Pathak PA, Roth AE (2013) Matching with couples: Stability and
  incentives in large markets. \emph{The Quarterly Journal of Economics} 128(4):1585--1632.

\bibitem[{Kurata et~al.(2017)Kurata, Hamada, Iwasaki, \protect\BIBand{}
  Yokoo}]{kurata2017controlled}
Kurata R, Hamada N, Iwasaki A, Yokoo M (2017) Controlled school choice with
  soft bounds and overlapping types. \emph{Journal of Artificial Intelligence Research} 58:153--184.


\bibitem[{Manjunath \protect\BIBand{} Turhan(2016)}]{manjunath2016}
  Manjunath, Vikram and Turhan, Bertan (2016) Two school systems, one district: What to do when a unified admissions process is impossible. \emph{Games and Economic Behavior} 95:25--40.


\bibitem[{MINEDUC(2018)}]{anuario}
MINEDUC (2018) Estadisticas de la educacion 2017. Report available at \url{https://centroestudios.mineduc.cl/wp-content/uploads/sites/100/2018/12/ANUARIO-MINEDUC_VERSION-BAJA.pdf}.

\bibitem[{Pycia \protect\BIBand{} Yenmez(2015)}]{pycia2015}
Pycia, M, Yenmez, M (2015) Matching with Externalities. \emph{Working paper}.


\bibitem[{Rios et~al.(2020)Rios, Larroucau, Parra, \protect\BIBand{}
  Cominetti}]{rios2020}
Rios, I, Larroucau, T, Parra, G, Cominetti, R (2020) Improving the Chilean College Admissions System. \emph{SSRN working paper}.


\bibitem[{Roth(1984)}]{roth1984}
Roth AE (1984) The {Evolution} of the labor market for medical interns and residents: A case study in Game Theory.
\emph{Journal of Political Economy} 92(6):991--1016.

\bibitem[{Roth \protect\BIBand{} Peranson(2002)}]{roth2002}
Roth, AE and Peranson, E (1984) The redesign of the matching market for American physicians: Some engineering aspects of economic design.
\emph{American Economic Review} 89:748--780.

\bibitem[{Roth et~al.(2004)Roth, S{\"{o}}nmez \protect\BIBand{} {\"{U}}nver(2002)}]{roth2004}
Roth, AE, S{\"{o}}nmez, T, {\"{U}}nver, MU (2004) Kidney Exchange.
\emph{Quarterly Journal of Economics} 119(2):457--488.

\bibitem[{S{\"{o}}nmez \protect\BIBand{} Switzer(2013)}]{somnez2013}
S{\"{o}}nmez, T, Switzer, TB (2004) Matching With (Branch‐of‐Choice) Contracts at the United States Military Academy.
\emph{Econometrica} 81(2):451--488.

\bibitem[{S{\"{o}}nmez \protect\BIBand{} Yenmez(2020)}]{sonmez2019}
S{\"{o}}nmez, T, Yenmez, MB (2019) Affirmative Action with Overlapping Reserves.
\emph{Working paper}.

\bibitem[{Valenzuela et~al.(2014)Valenzuela, Bellei, \protect\BIBand{} De~los
  R{\'\i}os}]{valenzuela2014socioeconomic}
Valenzuela JP, Bellei C, De~los R{\'\i}os D (2014) Socioeconomic school
  segregation in a market-oriented educational system. The case of Chile.
  \emph{Journal of Education Policy} 29(2):217--241.

\bibitem[{Villalobos \protect\BIBand{}
  Valenzuela(2012)}]{villalobos2012polarizacion}
Villalobos C, Valenzuela JP (2012) Polarizaci{\'o}n y cohesi{\'o}n social del
  sistema escolar chileno. \emph{Revista de An{\'a}lisis Econ{\'o}mico} 27(2):145--172.

\bibitem[{Wormald et~al.(2012)Wormald, Flores, Sabatini, Trebilcock,
  \protect\BIBand{} Rasse~Figueroa}]{wormald2012cultura}
Wormald G, Flores C, Sabatini F, Trebilcock MP, Rasse~Figueroa A (2012) Cultura
  de cohesi{\'o}n e integraci{\'o}n en las ciudades chilenas. \emph{Revista INVI} 27(76):117--145.

\end{thebibliography}
